\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

In all our experiments, \name{} has the highest Micro $AUC_p$,
demonstrating that \name{} can improve over other methods in the task
of identifying drugs that target a specific protein. \name{}

(i.e., higher MacroAUC
when evaluated on a drug--target split compared to a protein split;
large differences in macro- and micro measures)

>>>>

In all our experiments, \name{} has the highest Micro $AUC_p$,
demonstrating that \name{} can improve over other methods in the task
of identifying drugs that target a specific protein. Several methods
achieve a higher Macro AUC than \name{}, in particular when evaluated
using a drug--target pair splitting scheme; our results with the
``na\"ive'' prediction method show that it may be possible that models
trained on a drug--target split utilize certain biases in the dataset
without necessarily producing novel biological insights.
